### 2016-07-10 Docs/managing_jobs/managingjobs.tex
some notes on yt at NERSC

The preferred compilers on Titan are the Cray compilers.  
Cray 8.2.5 works well on titan/OLCF with MPI/OpenMP.

@@

To chain jobs, such that one queues up after the previous job finished,
use the {\tt chainslurm.sh} script in that same directory.

@@

>>>>

The preferred compilers on Titan are the Cray compilers.  
Cray 8.4.0 works well on titan/OLCF with MPI/OpenMP.

@@

To chain jobs, such that one queues up after the previous job finished,
use the {\tt chainslurm.sh} script in that same directory. You can view
the job dependency using:
\begin{verbatim}
squeue -l -j job-id
\end{verbatim}
where {\tt job-id} is the number of the job.

@@

\yt\ can be built using the {\tt install\_script.sh}.  It has been
tested using the build of {\tt yt} from source and dependencies via conda,
by setting:
\begin{verbatim}
INST_CONDA=1
INST_YT_SOURCE=1
\end{verbatim}
in the {\tt install\_script.sh}.  Once these are set, run:
\begin{verbatim}
source install_script.sh
\end{verbatim}
Note: installation was done in the home directory.

This way of building \yt\ installs it's own python and support
libraries in a directory, {\tt yt-conda}.  You need to make sure that
your start-up files (typically {\tt .bashrc.ext} at NERSC) don't {\tt
  module load} python or any python libraries, as this will interfere
with the conda installation.  The install script will direct you to
add the install location to your path.

At the moment, it seems that this does not actually build the yt source,
so a second step is needed, in {\tt yt-conda/bin/src/yt-hg}, do
\begin{verbatim}
python setup.py develop --user
\end{verbatim}
